---
title: "Jaishani's Portfolio"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    orientation: columns
    vertical_layout: fill
    
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(ggplot2)
library(cowplot)
```


Introduction
=========================================



THIS WILL BE INTRODUCTION TEXT, I THINK.....
..
...
...

Visualization {.storyboard}
========================================



### Chromogram

```{r}

```

-----------------------------------------------

Intro (0:00-0:11): The song begins with a brief intro featuring a repeating melody and Rihanna's vocals. Verse 1 (0:11-0:33): The first verse begins with Rihanna's vocals over a sparse beat, building to a more intense chorus. Chorus 1 (0:33-0:56): The first chorus features Rihanna's catchy hook " Come Mr. DJ song pon de replay," over a driving beat. Verse 2 (0:56-1:17): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:17-1:41): The second chorus is a repeat of the first chorus. Bridge (1:41-2:02): The bridge provides a contrast to the chorus, featuring a different melody and lyrics Chorus 3 (2:02-2:26): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:26-3:18): The song ends with a fade-out of the chorus, featuring Rihanna's vocals and a repeating synth melody.

### SSM



Intro (0:00-0:19): The song begins with a slow and mournful piano melody, which sets the tone for the emotional lyrics that follow. Verse 1 (0:19-0:41): The first verse begins with Rihanna's vocals over a simple piano accompaniment, building to a more intense chorus. Chorus 1 (0:41-1:02): The first chorus features Rihanna's emotive vocals over a more layered and complex instrumental accompaniment. Verse 2 (1:02-1:24): The second verse features a similar structure to the first verse, building to the second chorus. Chorus 2 (1:24-1:45): The second chorus is a repeat of the first chorus, with slight variations in the instrumentation and vocal delivery. Bridge (1:45-2:06): The bridge provides a contrast to the chorus, featuring a different melody and lyrics, as Rihanna sings "I don't wanna be the reason why / Every time I walk out the door / I see him die a little more inside." Chorus 3 (2:06-2:27): The third chorus is a repeat of the first two choruses, with a few variations in the instrumentation. Outro (2:27-3:51): The song ends with a repetition of the intro's piano melody, with Rihanna's vocals fading out.

### Tempogram
```{r}

```


Intro (0:00-0:10): The song begins with a synth chord progression and a simple drum pattern. Verse 1 (0:10-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus. Pre-chorus (0:43-1:02): The pre-chorus begins with a slightly more intense instrumental accompaniment. Chorus 1 (1:02-1:32): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:32-2:06): The second verse is similar to the first verse, but with slight variations in the instrumentation and vocal delivery. Pre-chorus (2:06-2:25): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:25-2:56): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:56-3:18): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression.Chorus 3 (3:18-3:49): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:49-4:13): The song ends with a repetition of the chorus and an instrumental fade-out.

### Dendogram




Intro (0:00-0:11): The song starts with a drum loop, a synth riff, and Rihanna's vocals.Verse 1 (0:11-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus.Pre-chorus (0:43-0:59): Starts with a more intense instrumental accompaniment.Chorus 1 (0:59-1:30): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment. Verse 2 (1:33-2:05): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:05-2:21): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:21-2:51): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal. Bridge (2:51-3:23): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Chorus 3 (3:23-3:53): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:53-4:16): The song ends with a repetition of the chorus and an instrumental fade-out.



### Chordogram


Intro (0:00-0:11): The song starts with a drum loop, a synth riff, and Rihanna's vocals.Verse 1 (0:11-0:43): The first verse features Rihanna's vocals over a sparse instrumental accompaniment, building to a pre-chorus.
Pre-chorus (0:43-0:59): Starts with a more intense instrumental accompaniment.Chorus 1 (0:59-1:30): The first chorus features a catchy and repetitive melody, with Rihanna's vocals over a layered and upbeat instrumental accompaniment.Verse 2 (1:33-2:05): The second verse is similar to the first verse, but with some variations in the instrumentation and vocal delivery. Pre-chorus (2:05-2:21): The pre-chorus is repeated, leading into the second chorus. Chorus 2 (2:21-2:51): The second chorus is a repeat of the first chorus, but with some variations in the instrumentation and vocal ad-libs. Bridge (2:51-3:23): The bridge provides a contrast to the chorus, with a slower tempo and a different chord progression. Chorus 3 (3:23-3:53): The third chorus is a repeat of the first two choruses, with additional vocal ad-libs and harmonies. Outro (3:53-4:16): The song ends with a repetition of the chorus and an instrumental fade-out.




Discussion 
=========================================
sdadsa